\documentclass{aifyp}

\usepackage{multicol}
\usepackage{cite}
\usepackage{graphicx} \usepackage[bottom]{footmisc}
\usepackage[section]{placeins} \raggedbottom{}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[hidelinks]{hyperref}
\usepackage{float}
\usepackage{qtree}
\usepackage{array,hhline}
\usepackage[ruled,vlined]{algorithm2e}

\usepackage{pdflscape}
\usepackage{afterpage}


\title{Automatic User Profiling for Intelligent
Tourist Trip Personalisation} 
\author{Liam Attard}

\graphicspath{ {./assets/} }

\supervisor{Dr Josef Bajada}
\date{June 2021} 

\longabstract{

     The objective of holiday activity planning is to maximise the
    traveller's enjoyment during such trips by selecting the right places to
    visit and things to do according to the person's preferences. This process
    involves preparing information from various data sources, which is often
    very time-consuming. This project presents a tourist itinerary
    recommendation algorithm that assists users by autonomously generating a
    personalised holiday plan according to the user's travel dates and
    constraints.  Furthermore, the system automatically builds a travel
    interest profile from the user's social media presence, which is then used
    to recommend itineraries tailored to the user's interests. The system uses
    social media APIs from popular platforms such as Facebook and Instagram.
    With the user's permission, the system gathers information such as pages
    the user likes and pictures posted by the user. 

    A Convolution Neural Network  is used to classify the user's pictures into their respective
    travel category, such as Beach, Clubbing, Nature, Museums or Shopping,
    which is then used to determine the user's predominant travel interest
    topics. A Resnet-18, Resnet-50 and Keras Sequential model are validated 
    separately on a testing dataset to see which one works best.  This computed
    travel profile of a user takes the form of a weight vector, which is then
    used to generate an automated itinerary that fits the user's preferences
    and travel constraints. 

    This weight vector is used to formulate a
    personalised objective function used by various meta-heuristic and
    evolutionary algorithms to optimise the plan. The algorithms consider hard
    constraints such as holiday dates, distances between places, and soft
    constraints (preferences), such as the interests and the user's preferred
    pace. This dissertation compares Particle Swarm Optimisation and Genetic
    Algorithms, and they are evaluated for both their plan quality and
    performance.

Since the results are highly personalised, the system was packaged into an
application that allows users to connect with their social media accounts,
build a personalised travel plan for a holiday in Malta, and ask the user to
assess the plan's quality with respect to personal preferences and activity pace. The
user is also asked to assess a more generic holiday itinerary without
specification of the generated plan, in order to assess the
effectiveness of the personalised holiday planning algorithm. }

\acknowledgement{I want to thank the following people for helping with this research project:

First, I would like to thank Dr Josef Bajada for guiding me positively
throughout this dissertation and always making me feel confident in my
abilities. Second, I would also like to thank Kelcy De Marco for all her patience, love
and support. Finally, I would like to thank my parents, siblings and friends
who have supported and motivated me consistently throughout this project.}

\begin{document} 

\input{sections/TableOfContents.tex}

\input{sections/introduction/intro.tex}

\pagebreak
\input{sections/lit_rev/intro.tex}

\pagebreak
\input{sections/methodology/intro.tex}

\pagebreak
\input{sections/results/intro.tex}
\pagebreak

\input{sections/results/conclusion.tex}
\pagebreak

\bibliographystyle{IEEEtran}
\bibliography{/home/liam/Documents/latex/library/bibFile/library.bib}

\input{sections/results/ack.tex}
\pagebreak

\end{document}

